Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-19 automatica/paper.tex
described experimental objectives
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{Lucas: describe here the experimental objectives.}

>>>>

Using the state-space models given in Section~\ref{exp:benchmarks}, 
our evaluation has the following two experimental goals:

\begin{enumerate}

\item[EG1] \textbf{(Performance)} Show that both the multi-staged and the abstraction-based
CEGIS approaches are able to generate FWL digital controllers using floating-point arithmetic 
in a reasonable amount of time.

\item[EG2] \textbf{(sanity check)} Confirm the
stability and safety of the synthesized controllers outside of our model.
